Exp 2 of 4

### 2016-08-13 experiments/e2/writeup/e2-b-knitr.Rnw
tidying up

\documentclass[a4paper,12pt]{article}
\usepackage[margin=2cm]{geometry}
\usepackage{placeins}

\title{Exp 2 of 4}
\begin{document}

<<setup, include=FALSE, cache=FALSE>>=
library(knitr)
options(formatR.arrow=TRUE, 
        width=100)
opts_chunk$set(fig.path='figure/graphics-', 
               cache.path='cache/graphics-', 
               fig.align='center', 
               dev='pdf', 
               fig.width=5, 
               fig.height=5, 
               fig.show='hold', 
               cache=FALSE, 
               par=TRUE,
               size='scriptsize',
               tidy=TRUE,
               comment = NA,
               tidy.opts = list(blank=FALSE, 
                                width.cutoff=100))
knit_hooks$set(crop=hook_pdfcrop)
@

@@

<<showCompression, fig.width=6, fig.height=4, fig.pos='hbtp', fig.cap='Ratios for different numbers of dots in the arrays: smaller values are more discriminable. Blue is for the ratio between the smallest number in the array and the largest number in an array. Red is for the mean of two ratios, one for the smallest number to the middle number, the other for the middle number to the largest number in the array', echo=FALSE>>=
#  Show compression of ratios of numbers of dots in the items
discriminability = sort(unique(as.numeric(dd$discriminability)))
plot(y=c(1.5,1.5,1.5,1.5), 
     x=discriminability, 
     ylab='',
     xlab='',
     yaxt='n',
     type='n', 
     xaxt='n',
     axes=F)
lines(y=c(1.5,1.5,1.5,1.5), x=discriminability, type='o', pch=19)
text(y=c(1.15,1.15,1.15,1.15), x=discriminability, labels=round(discriminability,2),  cex=.7)
mtext('mean (ratio min/med,\nratio med/max)', side = 2, line = 1)
mtext('Discriminability index', side=1, line=3)
mtext('Discriminability for each item', side=3, line=1, cex=1.5)
axis(1)
box(col='grey')
#text(y=1.00, x=0.07, labels="mean\n(ratio min/med,\nratio med/max)", col='red')
# axis(1, at=seq(-.1, 1,0.1)[4:11])
# axis(1)
@

@@

<<plotDistFreqPolys, fig.width=6, fig.height=4, fig.cap='Compare distributions of the various transformations of RT against random samples from normal distributions with the same mean and sd to see which transformations best approximate normal distributions', fig.pos='hbtp', fig.align='center', message=FALSE, warning=FALSE, echo=FALSE>>=
temp <- reshape2::melt(dat_transforms, 
                       id.vars=c("dfSubset", "RTtype", "Item", "Vagueness", "Number", "Quantity", "Order"),
                       measure.vars=c("RT_log", "RT_raw"),
                       variable.name="transformation",
                       value.name="time")
ggplot(temp, aes(time, colour=RTtype)) + 
  geom_freqpoly() + 
  facet_wrap(transformation~dfSubset, scales='free', ncol=4, nrow=1) + 
  scale_color_manual('RT Type: ', values=c("blue","red")) + 
  theme_bw() + 
  theme(aspect.ratio=1, 
        text=element_text(family='CMU Serif', size=10, face='plain'),
        axis.title.x=element_blank(),
        axis.text.x=element_text(angle=25),
        panel.grid=element_blank(),
        legend.position='top',
        legend.key=element_rect(color = 'white'))
@

<<plotBoxPlots, fig.width=6, fig.height=4, fig.cap='Show how transformations of RT affect distribution of times, and how they affect which times are outliers.', fig.pos='hbtp', echo=FALSE>>=
load('data_processed.Rda')
# allow reference to transformation
subdata = reshape2::melt(dd,
                         measure.vars=c("RT_log", "RT_raw"),
                         variable.name="transformation",
                         value.name="value") 
# boxplots for subjects and items separately for each dependent variable
ggplot(subdata) + 
  facet_wrap(~ transformation, scales="free", ncol=2, nrow=1) +
  geom_boxplot(aes(y=value, x=Item, col="Items"), outlier.colour = "black", outlier.shape = 21, outlier.size=0.1) + 
  geom_boxplot(aes(y=value, x=Subject, col="Subjects"), outlier.colour = "black", outlier.shape = 21, outlier.size=0.1) + 
  theme_bw() +
  theme(aspect.ratio=1, 
        text=element_text(family='CMU Serif', size=10, face='plain'),
        panel.grid=element_blank(),
        axis.ticks.x=element_blank(),
        axis.text.x=element_blank(),
        legend.position='top',
        legend.key=element_rect(color = 'white')) + 
  scale_colour_manual("",values=c("Items"="orange","Subjects"="blue")) +
  xlab("") + ylab("")
@

<<plotFastSlowRTs, fig.width=6, fig.height=4, fig.cap='Show how mean times for individual subjects and items vary with respect to the grand mean Log RT.', fig.pos='hbtp', message=FALSE, echo=FALSE>>=
# Show how mean times for individual subjects and items vary with respect to the grand mean RT.
subs=ddply(dd, .(level=Subject), 
           summarise, effect="subject", emean=mean(dd$RT_log), lmean=mean(RT_log),
           ldiff=mean(RT_log)-mean(dd$RT_log))
subs$level=1:30
subs$effect <- factor(subs$effect, levels=c("subject", "discriminability"))
itms=ddply(dd, .(level=discriminability), 
           summarise, effect="discriminability", emean=mean(dd$RT_log), lmean=mean(RT_log), 
           ldiff=mean(RT_log)-mean(dd$RT_log))
itms$effect <- factor(itms$effect, levels=c("subject", "discriminability"))
si=rbind(subs,itms)
si$effect <- factor(si$effect, levels=c("subject", "discriminability"))
my1 <- xyplot(data=si, lmean~level | effect, 
              aspect=1,
              layout=c(2,1),
              ylim = extendrange(si$lmean, f = 0.10),
              par.settings=list(trellis.par.set(superpose.symbol = list(col='black'), 
                                                superpose.line=list(col='black'))),
              xlab=NULL,
              ylab='Log RT',
              #main='How mean times for individual subjects and items\nvary with respect to the grand mean Log RT',
              mean=unique(si$emean),
              scales=list(x=list(relation="free", at=NULL, 
                                 labels=list("subject number", "item identifier"), cex=1 ),
                          y=list(at = c(0, 7, unique(si$emean), 8, 9),
                                 labels=c("0", "7", "Mean", "8", "9"))),
              panel=function(x,y,type,subscripts,...){
                panel.abline(h=unique(si$emean), col="lightgrey",lty=1,...)
                panel.arrows(x0=x, y0=unique(si$emean), x1=x, y1=y, subscripts=subscripts, code=3, length=0, ...)
                panel.xyplot(x,y,type='p', pch=21, cex=.5, col='black', fill='black', subscripts=subscripts,...)
              }
) # end of my1
my2 <- xyplot(data=si, ldiff~level | effect, 
              aspect=1, type='n',
              ylab="Deviation from\nmean Log RT",
              ylim=extendrange(si$ldiff,f=0.10)
) # creates a second y-axis scale
print(doubleYScale(my1, my2, 
                   add.axis=TRUE, 
                   add.ylab2=TRUE, 
                   use.style=FALSE))
@

<<plotMainsa, fig.width=6, fig.height=4, fig.cap='Plot main effects on several transformations', fig.pos='hbtp', message=FALSE, echo=FALSE, warning=FALSE>>=
# plot main effects on observed data
# allow reference to transformation
temp <- reshape2::melt(dd,
                       id.vars=c("Item", "Vagueness", "Number", "Quantity", "Order"),
                       measure.vars=c("RT_log",  "RT_raw"),
                       variable.name="transformation",
                       value.name="score")
# allow reference to effect
temp2 <- reshape2::melt(temp,
                        id.vars=c("transformation", "score"),
                        measure.vars=c("Item", "Vagueness", "Number", "Quantity", "Order"),
                        variable.name="effect",
                        value.name="level")
# do the plot
ggplot(temp2, aes(y=score, x=level, group=1, col=effect)) +
  facet_wrap(~transformation + effect, scales="free", ncol=5) +
  stat_summary(fun.data=mean_cl_normal, geom="pointrange") +
  stat_summary(fun.y=mean, geom="line") +
  theme_bw() +
  theme(aspect.ratio=1, 
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        axis.text.x = element_text(angle = 45, hjust = 1, size=8),
        legend.position="none") +
  ylab('Response latency\n') + xlab('')
@

<<mainB, fig.width=6, fig.height=4, fig.cap='Just the main effects', fig.pos='hbtp', message=FALSE, echo=FALSE>>=
# prep main effects rts data frame
vrts <- cbind(Effect="Vagueness",x=factor(c(1,2)),summarySEwithin(dd, measurevar="RT_log", withinvars=c("Vagueness")));names(vrts)[3]<-"Levels"
nrts <- cbind(Effect="Number",x=factor(c(1,2)), summarySEwithin(dd, measurevar="RT_log", withinvars=c("Number")));names(nrts)[3]<-"Levels"
qrts <- cbind(Effect="Quantity",x=factor(c(1,2)), summarySEwithin(dd, measurevar="RT_log", withinvars=c("Quantity")));names(qrts)[3]<-"Levels"
orts <- cbind(Effect="Order",x=factor(c(1,2)), summarySEwithin(dd, measurevar="RT_log", withinvars=c("Order")));names(orts)[3]<-"Levels"
irts <- cbind(Effect="Item",x=factor(c(1,2,3,4)), summarySEwithin(dd, measurevar="RT_log", withinvars=c("Item")));names(irts)[3]<-"Levels"
rts=rbind(vrts,nrts,qrts,orts)
rts$mins=rts$RT_log-rts$ci
rts$maxs=rts$RT_log+rts$ci
# plot main effects
ggplot(rts, aes(y=RT_log, x=Levels, group=1, ymin=mins, ymax=maxs)) +
  geom_line() +
  geom_errorbar(width=.05) +
  geom_point(pch=19) +
  facet_grid(~Effect, scale="free_x") +
  theme_bw() +
  theme(aspect.ratio=1,
        axis.text.x = element_text(size=8),
        axis.text.y = element_text(size=8, angle=15),
        panel.grid=element_blank()) +
  ylab("RT (log)") + xlab('')
@

<<mainD, fig.width=6, fig.height=5, fig.cap='Main effects over item ratios', fig.pos='hbtp', message=FALSE, echo=FALSE>>=
nrts <- cbind(Effect="Number",
              xlev=factor(c(1,2)), 
              myshape='a',
              summarySEwithin(dd, measurevar="RT_log", withinvars=c("discriminability","Number")))
names(nrts)[5]<-"Levels"

@@

p1=
  ggplot(data=rts, aes(x=discriminability, y=RT_log, group=Levels)) +
  geom_errorbar(data=droplevels(subset(rts, Effect=='Number')),width=.01, aes(ymin=mins, ymax=maxs)) +
  geom_line(data=droplevels(subset(rts, Effect=='Number'))) +
  geom_point(data=droplevels(subset(rts, Effect=='Number')),
             aes(shape=Levels, fill=Levels), size=3 ) +
  geom_errorbar(data=droplevels(subset(rts, Effect=='Order')), width=.01, aes(ymin=mins, ymax=maxs)) +
  geom_line(data=droplevels(subset(rts, Effect=='Order'))) +
  geom_point(data=droplevels(subset(rts, Effect=='Order')),
             aes(shape=Levels, fill=Levels), size=3  ) +
  geom_errorbar(data=droplevels(subset(rts, Effect=='Quantity')),width=.01, aes(ymin=mins, ymax=maxs)) +
  geom_line(data=droplevels(subset(rts, Effect=='Quantity'))) +
  geom_point(data=droplevels(subset(rts, Effect=='Quantity')),
             aes(shape=Levels, fill=Levels), size=3  ) +
  geom_errorbar(data=droplevels(subset(rts, Effect=='Vagueness')),width=.01, aes(ymin=mins, ymax=maxs)) +
  geom_line(data=droplevels(subset(rts, Effect=='Vagueness'))) +
  geom_point(data=droplevels(subset(rts, Effect=='Vagueness')),
             aes(shape=Levels, fill=Levels), size=3  ) +
  facet_grid(~Effect) +
  scale_shape_manual(values = c(
    "Numeric"=21,
    "Verbal"=21,
    "LtoR"=22,
    "RtoL"=22,
    "Small"=23,
    "Large"=23,
    "Crisp"=24,
    "Vague"=24),
    breaks=c('Numeric','Verbal','LtoR','RtoL','Small','Large','Crisp','Vague'))  +
  scale_fill_manual(values = c(
    "Numeric"="black",
    "Verbal"="white",
    "LtoR"="black",
    "RtoL"="white",
    "Small"="black",
    "Large"="white",
    "Crisp"="black",
    "Vague"="white"),
    breaks=c('Numeric','Verbal','LtoR','RtoL','Small','Large','Crisp','Vague')) +
  scale_x_continuous(minor_breaks=NULL,
                     breaks=1-c(0.5125000, 0.6876471, 0.7691558, 0.8166667),
                     labels=abbreviate(1-c(0.5125000, 0.6876471, 0.7691558, 0.8166667))) +
  theme_bw() +
  theme(aspect.ratio=1,
        legend.position='top',
        axis.text.x=element_text(size=8, angle=35),
        axis.text.y=element_text(size=8, angle=15),
        legend.key=element_rect(color = 'white')
        #,        panel.grid=element_blank()
        ) +
  ylab("RT (log)") + xlab("Item discriminability measure")
p1
@

<<22way, fig.width=7, fig.height=7, fig.cap='2-way interactions over item ratios', fig.pos='hbtp', message=FALSE, echo=FALSE>>=
# prep 2 ways over items rts data frame
rts1 <- summarySEwithin(dd, measurevar="RT_log", withinvars=c("discriminability", "Vagueness","Number")); names(rts1)[2] <- "F1"; names(rts1)[3] <- "F2"
rts1$E1 <- "Vagueness"
rts1$E2 <- "Number"
rts2 <- summarySEwithin(dd, measurevar="RT_log", withinvars=c("discriminability", "Vagueness","Quantity")); names(rts2)[2] <- "F1"; names(rts2)[3] <- "F2"
rts2$E1 <- "Vagueness"
rts2$E2 <- "Quantity"
rts3 <- summarySEwithin(dd, measurevar="RT_log", withinvars=c("discriminability", "Vagueness","Order")); names(rts3)[2] <- "F1"; names(rts3)[3] <- "F2"
rts3$E1 <- "Vagueness"
rts3$E2 <- "Order"
rts4 <- summarySEwithin(dd, measurevar="RT_log", withinvars=c("discriminability", "Quantity", "Number")); names(rts4)[2] <- "F1"; names(rts4)[3] <- "F2"
rts4$E1 <- "Quantity"
rts4$E2 <- "Number"
rts5 <- summarySEwithin(dd, measurevar="RT_log", withinvars=c("discriminability", "Order","Number")); names(rts5)[2] <- "F1"; names(rts5)[3] <- "F2"
rts5$E1 <- "Order"
rts5$E2 <- "Number"
rts6 <- summarySEwithin(dd, measurevar="RT_log", withinvars=c("discriminability", "Quantity","Order")); names(rts6)[2] <- "F1"; names(rts6)[3] <- "F2"
rts6$E1 <- "Quantity"
rts6$E2 <- "Order"
rts <- rbind(rts1,rts2,rts3,rts4,rts5,rts6)
rts$mins=rts$RT_log-rts$ci
rts$maxs=rts$RT_log+rts$ci
rts$discriminability <- as.numeric(as.character(rts$discriminability))
rts$F3 <- factor(paste(rts$F1,rts$F2))
rts$E1 <- factor(rts$E1, levels=c("Number","Order","Quantity","Vagueness"))
rts$E2 <- factor(rts$E2, levels=c("Number","Order","Quantity","Vagueness"))
# The palette with black:
cbbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
ggplot(rts, aes(y=RT_log, x=discriminability, group=F3, col=F2, pch=F1)) +
  facet_grid(E2~E1, drop=F) +
  geom_point() +
  geom_line() +
  theme_bw() +
  theme(
    aspect.ratio=1
    #,  panel.grid=element_blank()
    , axis.text.x=element_text(size=7, angle=45,hjust=1)
    , axis.text.y=element_text(size=7)
    ) +
  scale_color_manual(name="colour",values=cbbPalette) +
  scale_shape_discrete(name="shape") +
  #scale_x_continuous(breaks = round(sort(unique(rts$discriminability)),1)) +
  scale_x_continuous(minor_breaks=NULL,
                     breaks=1-c(0.5125000, 0.6876471, 0.7691558, 0.8166667),
                     labels=abbreviate(1-c(0.5125000, 0.6876471, 0.7691558, 0.8166667))) 
@

<<plotInt1, fig.width=6, fig.height=4, fig.cap='vagueness by number interaction over items', fig.pos='hbtp', message=FALSE, echo=FALSE>>=
rts <- summarySEwithin(dd, measurevar="RT_log", withinvars=c("Number","Vagueness","Item"))
rts$condition=paste(rts$Number,rts$Vagueness, sep= ' ')
dodge = position_dodge(width=0.2)
ggplot(rts, aes(y=RT_log, x=Item, ymin=RT_log-ci, ymax=RT_log+ci,
                group=condition, shape=condition, fill=condition)) +
  geom_line(position=dodge) +
  geom_errorbar(width=.2, position=dodge) +
  geom_point(size=4, position=dodge) +
  scale_shape_manual("",values = c(22, 22, 21, 21)) +
  scale_fill_manual("",values=c("black","white","black","white")) +
  ggtitle("Response time") +
  ylab("RT_log") +
  xlab("") +
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        legend.key = element_blank(), aspect.ratio=1,
        axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_grid(~Number) 
@

>>>>

\documentclass[a4paper,12pt,twoside]{article}
\usepackage[margin=2cm]{geometry}
\usepackage{placeins}
\usepackage{graphicx}
\usepackage{color}
\usepackage{hyperref}
\title{Exp 2 of 4}
\begin{document}

<<setup, include=FALSE, cache=FALSE>>=
library(knitr)
options(formatR.arrow=TRUE, 
        width=100)
opts_chunk$set(fig.path='figure/graphics-', 
               cache.path='cache/graphics-', 
               fig.align='center', 
               dev='pdf', 
               fig.width=5, 
               fig.height=5, 
               fig.show='hold', 
               cache=FALSE, 
               par=TRUE,
               size='scriptsize',
               tidy=TRUE,
               comment = NA,
               tidy.opts = list(blank=FALSE, 
                                width.cutoff=100))
#knit_hooks$set(crop=hook_pdfcrop)
@

@@

<<showCompression, fig.width=6, fig.height=4, fig.pos='hbtp', fig.cap='Ratios for different numbers of dots in the arrays: smaller values are more discriminable. Blue is for the ratio between the smallest number in the array and the largest number in an array. Red is for the mean of two ratios, one for the smallest number to the middle number, the other for the middle number to the largest number in the array', echo=FALSE>>=
#  Show compression of ratios of numbers of dots in the items
discriminability = sort(unique(as.numeric(dd$discriminability)))
plot(y=c(1.5,1.5,1.5,1.5), 
     x=discriminability, 
     ylab='',
     xlab='',
     yaxt='n',
     type='n', 
     xaxt='n',
     axes=F)
lines(y=c(1.5,1.5,1.5,1.5), x=discriminability, type='o', pch=19)
text(y=c(1.15,1.15,1.15,1.15), x=discriminability, labels=round(discriminability,2),  cex=.7)
mtext('mean (ratio min/med,\nratio med/max)', side = 2, line = 1)
mtext('Discriminability index', side=1, line=3)
mtext('Discriminability for each item', side=3, line=1, cex=1.5)
axis(1)
box(which='plot', col='grey')

#text(y=1.00, x=0.07, labels="mean\n(ratio min/med,\nratio med/max)", col='red')
# axis(1, at=seq(-.1, 1,0.1)[4:11])
# axis(1)
@

\clearpage
\subsection{Consider using log RT}

@@

<<plotDistFreqPolys, fig.width=6, fig.height=4, fig.cap='Compare distributions of the various transformations of RT against random samples from normal distributions with the same mean and sd to see which transformations best approximate normal distributions', fig.pos='hbtp', fig.align='center', message=FALSE, warning=FALSE, echo=FALSE>>=
temp <- reshape2::melt(dat_transforms, 
                       id.vars=c("dfSubset", "RTtype", "Item", "Vagueness", "Number", "Quantity", "Order"),
                       measure.vars=c("RT_log", "RT_raw"),
                       variable.name="transformation",
                       value.name="time")
ggplot(temp, aes(time, colour=RTtype)) + 
  geom_freqpoly() + 
  facet_wrap(transformation~dfSubset, scales='free', ncol=4, nrow=1) + 
  scale_color_manual('RT Type: ', values=c("blue","red")) + 
  theme_bw() + 
  theme(aspect.ratio=1, 
        text=element_text(family='CMU Serif', size=10, face='plain'),
        axis.title.x=element_blank(),
        axis.text.x=element_text(angle=25),
        panel.grid=element_blank(),
        legend.position='top',
        legend.key=element_rect(color = 'white'),
        plot.background=element_rect(fill=NA, color='white'))
@

\clearpage
\subsection{How logging RT affects the distribution}

<<plotBoxPlots, fig.width=6, fig.height=4, fig.cap='Show how transformations of RT affect distribution of times, and how they affect which times are outliers.', fig.pos='hbtp', echo=FALSE>>=
load('data_processed.Rda')
# allow reference to transformation
subdata = reshape2::melt(dd,
                         measure.vars=c("RT_log", "RT_raw"),
                         variable.name="transformation",
                         value.name="value") 
# boxplots for subjects and items separately for each dependent variable
ggplot(subdata) + 
  facet_wrap(~ transformation, scales="free", ncol=2, nrow=1) +
  geom_boxplot(aes(y=value, x=Item, col="Items"), outlier.colour = "black", outlier.shape = 21, outlier.size=0.1) + 
  geom_boxplot(aes(y=value, x=Subject, col="Subjects"), outlier.colour = "black", outlier.shape = 21, outlier.size=0.1) + 
  theme_bw() +
  theme(aspect.ratio=1, 
        text=element_text(family='CMU Serif', size=10, face='plain'),
        panel.grid=element_blank(),
        axis.ticks.x=element_blank(),
        axis.text.x=element_blank(),
        legend.position='top',
        legend.key=element_rect(color = 'white'),
        plot.background=element_rect(fill=NA, color='white')) + 
  scale_colour_manual("",values=c("Items"="orange","Subjects"="blue")) +
  xlab("") + ylab("")
@

\clearpage
\subsection{Identify fast and slow subjects and items}

<<plotFastSlowRTs, fig.width=6, fig.height=4, fig.cap='Show how mean times for individual subjects and items vary with respect to the grand mean Log RT.', fig.pos='hbtp', message=FALSE, echo=FALSE>>=
# Show how mean times for individual subjects and items vary with respect to the grand mean RT.
subs=ddply(dd, .(level=Subject), 
           summarise, effect="subject", emean=mean(dd$RT_log), lmean=mean(RT_log),
           ldiff=mean(RT_log)-mean(dd$RT_log))
subs$level=1:30
subs$effect <- factor(subs$effect, levels=c("subject", "discriminability"))
itms=ddply(dd, .(level=discriminability), 
           summarise, effect="discriminability", emean=mean(dd$RT_log), lmean=mean(RT_log), 
           ldiff=mean(RT_log)-mean(dd$RT_log))
itms$effect <- factor(itms$effect, levels=c("subject", "discriminability"))
si=rbind(subs,itms)
si$effect <- factor(si$effect, levels=c("subject", "discriminability"))
my1 <- xyplot(data=si, lmean~level | effect, 
              aspect=1,
              layout=c(2,1),
              ylim = extendrange(si$lmean, f = 0.10),
              par.settings=list(trellis.par.set(superpose.symbol = list(col='black'), 
                                                superpose.line=list(col='black'))),
              xlab=NULL,
              ylab='Log RT\n',
              #main='How mean times for individual subjects and items\nvary with respect to the grand mean Log RT',
              mean=unique(si$emean),
              scales=list(x=list(relation="free", at=NULL, 
                                 labels=list("subject number", "item identifier"), cex=1 ),
                          y=list(at = c(0, 7, unique(si$emean), 8, 9),
                                 labels=c("0", "7", "Mean", "8", "9"))),
              panel=function(x,y,type,subscripts,...){
                panel.abline(h=unique(si$emean), col="lightgrey",lty=1,...)
                panel.arrows(x0=x, y0=unique(si$emean), x1=x, y1=y, subscripts=subscripts, code=3, length=0, ...)
                panel.xyplot(x,y,type='p', pch=21, cex=.5, col='black', fill='black', subscripts=subscripts,...)
              }
) # end of my1
my2 <- xyplot(data=si, ldiff~level | effect, 
              aspect=1, type='n',
              ylab="Deviation from\nmean Log RT",
              ylim=extendrange(si$ldiff,f=0.10)
) # creates a second y-axis scale
print(doubleYScale(my1, my2, 
                   add.axis=TRUE, 
                   add.ylab2=TRUE, 
                   use.style=FALSE))
@

\clearpage
\subsection{Plot main effects in both transformations}

<<prepplotsMainEffects, message=FALSE, echo=FALSE, warning=FALSE>>=
# plot main effects on observed data
# allow reference to transformation
# raw
tempraw <- reshape2::melt(dd,
                          id.vars=c("Item", "Vagueness", "Number", "Quantity", "Order"),
                          measure.vars=c("RT_raw"),
                          variable.name="transformation",
                          value.name="score")
# allow reference to effect
tempraw2 <- reshape2::melt(tempraw,
                           id.vars=c("transformation", "score"),
                           measure.vars=c("Item", "Vagueness", "Number", "Quantity", "Order"),
                           variable.name="effect",
                           value.name="level")
# log
templog <- reshape2::melt(dd,
                          id.vars=c("Item", "Vagueness", "Number", "Quantity", "Order"),
                          measure.vars=c("RT_log"),
                          variable.name="transformation",
                          value.name="score")
# allow reference to effect
templog2 <- reshape2::melt(templog,
                           id.vars=c("transformation", "score"),
                           measure.vars=c("Item", "Vagueness", "Number", "Quantity", "Order"),
                           variable.name="effect",
                           value.name="level")
@

<<plotMainEffectsRaw, fig.width=6, fig.height=3, fig.cap='Plot main effects in raw RT', fig.pos='hbtp', echo=FALSE>>=
# raw
ggplot(tempraw2, aes(y=score, x=level, group=1, col=effect)) +
  facet_wrap(~effect, scales="free", ncol=5) +
  stat_summary(fun.data=mean_cl_normal, geom="pointrange") +
  stat_summary(fun.y=mean, geom="line") +
  theme_bw() +
  theme(aspect.ratio=1, 
        # axis.text.y=element_blank(),
        # axis.ticks.y=element_blank(),
        panel.grid=element_blank(),
        axis.text.x = element_text(angle = 45, hjust = 1, size=8),
        legend.position="none",
        plot.background=element_rect(fill=NA, color='white')) +
  xlab('')
@

<<plotMainEffectsLog, fig.width=6, fig.height=3, fig.cap='Plot main effects in log RT', fig.pos='htbp', echo=FALSE>>=
# log
ggplot(templog2, aes(y=score, x=level, group=1, col=effect)) +
  facet_wrap(~effect, scales="free", ncol=5) +
  stat_summary(fun.data=mean_cl_normal, geom="pointrange") +
  stat_summary(fun.y=mean, geom="line") +
  theme_bw() +
  theme(aspect.ratio=1, 
        # axis.text.y=element_blank(),
        # axis.ticks.y=element_blank(),
        panel.grid=element_blank(),
        axis.text.x = element_text(angle = 45, hjust = 1, size=8),
        legend.position="none",
        plot.background=element_rect(fill=NA, color='white')) +
  xlab('')
@

\clearpage
\subsection{Main effects in log RT over discriminability}

<<mainD, fig.width=6, fig.height=5, fig.cap='Main effects in log RT over discriminability', fig.pos='hbtp', message=FALSE, echo=FALSE>>=
nrts <- cbind(Effect="Number",
              xlev=factor(c(1,2)), 
              myshape='a',
              summarySEwithin(dd, measurevar="RT_log", withinvars=c("discriminability","Number")))
names(nrts)[5]<-"Levels"

@@

p1=
  ggplot(data=rts, aes(x=discriminability, y=RT_log, group=Levels)) +
  geom_errorbar(data=droplevels(subset(rts, Effect=='Number')),width=.01, aes(ymin=mins, ymax=maxs)) +
  geom_line(data=droplevels(subset(rts, Effect=='Number'))) +
  geom_point(data=droplevels(subset(rts, Effect=='Number')),
             aes(shape=Levels, fill=Levels), size=3 ) +
  geom_errorbar(data=droplevels(subset(rts, Effect=='Order')), width=.01, aes(ymin=mins, ymax=maxs)) +
  geom_line(data=droplevels(subset(rts, Effect=='Order'))) +
  geom_point(data=droplevels(subset(rts, Effect=='Order')),
             aes(shape=Levels, fill=Levels), size=3  ) +
  geom_errorbar(data=droplevels(subset(rts, Effect=='Quantity')),width=.01, aes(ymin=mins, ymax=maxs)) +
  geom_line(data=droplevels(subset(rts, Effect=='Quantity'))) +
  geom_point(data=droplevels(subset(rts, Effect=='Quantity')),
             aes(shape=Levels, fill=Levels), size=3  ) +
  geom_errorbar(data=droplevels(subset(rts, Effect=='Vagueness')),width=.01, aes(ymin=mins, ymax=maxs)) +
  geom_line(data=droplevels(subset(rts, Effect=='Vagueness'))) +
  geom_point(data=droplevels(subset(rts, Effect=='Vagueness')),
             aes(shape=Levels, fill=Levels), size=3  ) +
  facet_grid(~Effect) +
  scale_shape_manual(values = c(
    "Numeric"=21,
    "Verbal"=21,
    "LtoR"=22,
    "RtoL"=22,
    "Small"=23,
    "Large"=23,
    "Crisp"=24,
    "Vague"=24),
    breaks=c('Numeric','Verbal','LtoR','RtoL','Small','Large','Crisp','Vague'))  +
  scale_fill_manual(values = c(
    "Numeric"="black",
    "Verbal"="white",
    "LtoR"="black",
    "RtoL"="white",
    "Small"="black",
    "Large"="white",
    "Crisp"="black",
    "Vague"="white"),
    breaks=c('Numeric','Verbal','LtoR','RtoL','Small','Large','Crisp','Vague')) +
  scale_x_continuous(minor_breaks=NULL,
                     breaks=1-c(0.5125000, 0.6876471, 0.7691558, 0.8166667),
                     labels=abbreviate(1-c(0.5125000, 0.6876471, 0.7691558, 0.8166667))) +
  theme_bw() +
  theme(aspect.ratio=1,
        legend.position='top',
        axis.text.x=element_text(size=8, angle=35),
        axis.text.y=element_text(size=8, angle=15),
        legend.key=element_rect(color = 'white'),
        plot.background=element_rect(fill=NA, color='white')
        #,        panel.grid=element_blank()
        ) +
  xlab("Item discriminability measure")
p1
@

\clearpage
\subsection{2-Way interactions over discriminability}

<<22way, fig.width=7, fig.height=7, fig.cap='2-way interactions over discriminability', fig.pos='hbtp', message=FALSE, echo=FALSE>>=
# prep 2 ways over items rts data frame
rts1 <- summarySEwithin(dd, measurevar="RT_log", withinvars=c("discriminability", "Vagueness","Number")); names(rts1)[2] <- "F1"; names(rts1)[3] <- "F2"
rts1$E1 <- "Vagueness"
rts1$E2 <- "Number"
rts2 <- summarySEwithin(dd, measurevar="RT_log", withinvars=c("discriminability", "Vagueness","Quantity")); names(rts2)[2] <- "F1"; names(rts2)[3] <- "F2"
rts2$E1 <- "Vagueness"
rts2$E2 <- "Quantity"
rts3 <- summarySEwithin(dd, measurevar="RT_log", withinvars=c("discriminability", "Vagueness","Order")); names(rts3)[2] <- "F1"; names(rts3)[3] <- "F2"
rts3$E1 <- "Vagueness"
rts3$E2 <- "Order"
rts4 <- summarySEwithin(dd, measurevar="RT_log", withinvars=c("discriminability", "Quantity", "Number")); names(rts4)[2] <- "F1"; names(rts4)[3] <- "F2"
rts4$E1 <- "Quantity"
rts4$E2 <- "Number"
rts5 <- summarySEwithin(dd, measurevar="RT_log", withinvars=c("discriminability", "Order","Number")); names(rts5)[2] <- "F1"; names(rts5)[3] <- "F2"
rts5$E1 <- "Order"
rts5$E2 <- "Number"
rts6 <- summarySEwithin(dd, measurevar="RT_log", withinvars=c("discriminability", "Quantity","Order")); names(rts6)[2] <- "F1"; names(rts6)[3] <- "F2"
rts6$E1 <- "Quantity"
rts6$E2 <- "Order"
rts <- rbind(rts1,rts2,rts3,rts4,rts5,rts6)
rts$mins=rts$RT_log-rts$ci
rts$maxs=rts$RT_log+rts$ci
rts$discriminability <- as.numeric(as.character(rts$discriminability))
rts$F3 <- factor(paste(rts$F1,rts$F2))
rts$E1 <- factor(rts$E1, levels=c("Number","Order","Quantity","Vagueness"))
rts$E2 <- factor(rts$E2, levels=c("Number","Order","Quantity","Vagueness"))
# The palette with black:
cbbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
ggplot(rts, aes(y=RT_log, x=discriminability, group=F3, col=F2, pch=F1)) +
  facet_grid(E2~E1, drop=F) +
  geom_point() +
  geom_line() +
  theme_bw() +
  theme(
    aspect.ratio=1
    #,  panel.grid=element_blank()
    , axis.text.x=element_text(size=7, angle=45,hjust=1)
    , axis.text.y=element_text(size=7),
    plot.background=element_rect(fill=NA, color='white')
    ) +
  scale_color_manual(name="colour",values=cbbPalette) +
  scale_shape_discrete(name="shape") +
  #scale_x_continuous(breaks = round(sort(unique(rts$discriminability)),1)) +
  scale_x_continuous(minor_breaks=NULL,
                     breaks=1-c(0.5125000, 0.6876471, 0.7691558, 0.8166667),
                     labels=abbreviate(1-c(0.5125000, 0.6876471, 0.7691558, 0.8166667))) 
@

\clearpage
\subsection{Vagueness by number interaction over items}

<<plotInt1, fig.width=6, fig.height=4, fig.cap='vagueness by number interaction over items', fig.pos='hbtp', message=FALSE, echo=FALSE>>=
rts <- summarySEwithin(dd, measurevar="RT_log", withinvars=c("Number","Vagueness","Item"))
rts$condition=paste(rts$Number,rts$Vagueness, sep= ' ')
dodge = position_dodge(width=0.2)
ggplot(rts, aes(y=RT_log, x=Item, ymin=RT_log-ci, ymax=RT_log+ci,
                group=condition, shape=condition, fill=condition)) +
  geom_line(position=dodge) +
  geom_errorbar(width=.2, position=dodge) +
  geom_point(size=4, position=dodge) +
  scale_shape_manual("",values = c(22, 22, 21, 21)) +
  scale_fill_manual("",values=c("black","white","black","white")) +
  ggtitle("Response time") +
  ylab("RT_log") +
  xlab("") +
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        legend.key = element_blank(), aspect.ratio=1,
        axis.text.x = element_text(angle = 45, hjust = 1),
        plot.background=element_rect(fill=NA, color='white')) +
  facet_grid(~Number) 
@

\clearpage
\subsection{Vagueness by number interaction over discriminability}
